Long name of the paper

### 2018-08-17 anzjs2018/anzjs2018.tex
change sections

\begin{document}
\cleanlookdateon
\runningheads{Short title of paper}{TOM~ELLIOTT AND THOMAS~LUMLEY}
\title{Long name of the paper}
\author{Tom Elliott\corrauth and Thomas Lumley}
\affiliation{University of Auckland}
\address{
    Department of Statistics, University of Auckland,\\
    Private Bag 92019, Auckland 1142, New Zealand\\
    Email: \texttt{tom.elliott@auckland.ac.nz}
}

@@

\section{Transit network construction}
\label{sec:gtfs}

Before we can usefully model buses in real-tim{}e, 
we need to construct a \emph{transit network},
consisting of \emph{intersections} (nodes)
connected by \emph{road segments} (edges).
In this way, each \emph{route} 
(a journey taken by a transit vehicle, from an origin to a destination by a fixed path)
can be represented as a sequence of road segments,
each of which we model as vehicles travel along them (see section~\ref{sec:kf}).

>>>>

\begin{document}
\cleanlookdateon
\runningheads{Short title of paper}{TOM~ELLIOTT AND THOMAS~LUMLEY}
\title{Long name of the paper}
\author{Tom Elliott\corrauth~and~Thomas~Lumley}
\affiliation{University of Auckland}
\address{
    Department of Statistics, University of Auckland,\\
    Private Bag 92019, Auckland 1142, New Zealand\\
    Email: \texttt{tom.elliott@auckland.ac.nz}
}

@@

\section{Working with GTFS data}
\label{sec:gtfs}

What is GTFS? Its purpose. Its accessibility (global, free).
Thus a good thing to use.

\subsection{Transit network construction}
\label{sec:network_build}

Before we can usefully model buses in real-time, 
we need to construct a \emph{transit network},
consisting of \emph{intersections} (nodes)
connected by \emph{road segments} (edges).
In this way, each \emph{route} 
(a journey taken by a transit vehicle, from an origin to a destination by a fixed path)
can be represented as a sequence of road segments,
each of which we model as vehicles travel along them (see section~\ref{sec:kf}).

\subsection{Realtime vehicle locations}
\label{sec:realtime_data}

Recieve vehicle updates ~30 seconds (but the actual update frequency varies continually, even for a single bus).
Key features of the data - position, trip, timestamp, etc.
Also note there is trip updates feed, but this is less useful (the arrival/departure times themselves haven't proved reliable).
